---
title: "Migration PNAD - 2001-2015"
author: "Guilherme M. Dutra"
date: "31 December 2021"
output:
  html_notebook:
    toc: yes
    number_sections: yes
    toc_float: yes
  html_document:
    toc: yes
    df_print: paged
subtitle: 2nd WB-UNHCR Forced Displacement Conference
---

```{r import, include=FALSE}
rm(list = ls())
source("import_code.R", local = knitr::knit_global())
```
<br>
Migration variables are analysed in three steps:

- _Population_ - overview of the population covered in the region
- _Respondents in the Southeast_ - filtering for respondents in the Southeast Region, in order to estimate immigration to the Southeast
- _Respondents with state of origin in the Northeast_ - identifying respondents who are original from the Northeast, in order to estimate emmigration from that region

*2010 is a census year so not included in the analysis (estimates to be included later)*

# V0502 - Nasceu nesta UF

## V0502_POP - Population
### Change 2001-2015

```{r}

```

## V0502_SE - Respondents in the Southeast

## V0502_NE - State of origin - Northeast




Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

